\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-22 DrC Version 1/root1.tex
Revision by Dr.C & Qianli

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
%\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
\usepackage{mathtools}   % loads Â»amsmathÂ«
\usepackage{amssymb,amsmath}
\usepackage{amsfonts}
\usepackage{color}

@@

%In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem. Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams. A probabilistic method is presented to solve the homogeneous matrix equations without a priori knowledge of the correspondence. Using the Euclidean-Group invariants, an exact solution can be found. For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
Calibration is often an important and necessary step in the use of image-guided systems. In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control. As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony in sampling rates and processing time. One common scenario is a constant shift between the two data streams. Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$s and $B$s. We begin by discussing probability density functions on $SE(3)$ and then introduce Euclidean-group invariants to obtain an exact solution for $X$ and $Y$. Then, we present a method to simultaneously recover $X$ and $Y$ and the correspondence between the shifted data sets. Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness.

@@

In the $\textbf{AX=YB}$ problem, data streams of $A$s and $B$s can be respectively obtained via different sensors. The data streams may arrive in an asynchronous fashion due to the different working frequencies of the sensors. This asynchrony causes a shift between the two data streams which removes the correspondence between the $A$s and $B$s. In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$s and $B$s.

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem formulated as AX=YB. (2) The hand-eye calibration problem formulated as AX=XB. Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems. (The Universal Robot pictured above is owned by Prof. Emad Boctor of Johns Hopkins University). Note: the $A$ and $B$ in the above two problems have different physical meanings. One is the absolute transformation and the other is relative transformation as can be seen in the figures. 
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,rovelo2008geometric, fassi2005hand,zhao2011hand,ackerman2014online}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the litefit rature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative, ernst2012non,strobl2006optimal,li2010simultaneous,shah2013solving,heller2014hand}. Simulatneous calibration %s
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a priori. In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

The rest of the paper is organized as follows. In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$. In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. In Section \ref{sect5}, we briefly discuss the case where one can obtain $\left( X, Y \right)$ without recovering the correspondence between the data sets.
Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.

@@

Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for the group element.

@@

\begin{equation}\label{equ1}
A_{i}X=YB_{i}.
\end{equation}
For a group element $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere:

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I.
\end{array}
\right.
\end{equation}
The Dirac delta function also satisfies the identity constraint as:

@@

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given $K,H \in SE(3)$ and two well-defined functions $f_{1}, f_{2} \in \left(L^1 \cap L^2 \right)(SE(3))$, their convolution on $SE(3)$ is defined as:

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK.
\end{equation}
where $\circ$ denotes the group product, and in this case it is simply matrix multiplication. Employing the properties of the $\delta$ function, it is straightforward to see that:

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}
Defining the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

@@

If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''. The convolution of two highly-focused PDFs have some interesting properties that can be used to solve for $X$.
For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used. In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic} as:

\begin{equation}
log(H) = \widehat{\bf h} 
=
\left(
\begin{array}{cccc}
   0 & -h_3 &  h_2 & h_4 \\ 
 h_3 &    0 & -h_1 & h_5 \\
-h_2 & -h_1 &    0 & h_6 \\
   0 &    0 &    0 &  0 
\end{array}
\right)
\end{equation}
where ${\bf h} = log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element ($se(3)$) of $H$.

@@

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}log^{\vee}(M_A^{-1}A_i)[log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

\begin{equation}\label{equ13}
    ^{k+1}M_{A} = ^{k}M_{A} \circ exp[\frac{1}{n}\sum_{i=1}^{n}log(^{k}M_{A}^{-1}\circ A_{i})]
\end{equation}

An initial estimate of the iterative procedure can be chosen as $^{0}M_{A}=\frac{1}{n}\sum_{i=1}^{n}log(A_{i})$, then a local minimum of $M_A$ is obtained by solving a nonlinear optimization problem with the cost function of $|| \sum_{i=1}^{n}log(M_{A}^{-1}A_{i}) ||^{2}$. A similar procedure can be used to compute $M_B$. $\Sigma_A$ and $\Sigma_B$ are then straight forward to compute given known $M_A$ and $M_B$.

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{wang2008nonparametric}:

\begin{IEEEeqnarray}{l}\label{equ14}
M_{1 \ast 2} = M_{1}M_{2} \IEEEyessubnumber
\\*
\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2}. \IEEEyessubnumber
\end{IEEEeqnarray}
where

$$Ad(H)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right).$$

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively. Therefore, the following equations can be obtained using Eq.~\ref{equ14}:

\begin{IEEEeqnarray}{l}
M_{A} X = Y M_{B} \IEEEyessubnumber\label{equ15a}
\\*
Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B}. \IEEEyessubnumber\label{equ15b}
\end{IEEEeqnarray}

To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:

@@

\begin{equation}\label{equ18}
    \Lambda = (Q_{M_{A}}^{T}R_{X}^{T}Q_{M_{B}}) \Lambda (Q_{M_{B}}^{T}R_{X}Q_{M_{A}})= P \Lambda P^{T}
\end{equation}
where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the rotation matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).

\begin{equation}\label{equ_P}
\left\{
\begin{array}{l}
P^{T} = P^{-1} \\
det(P) = \pm 1.
\end{array}
\right.
\end{equation}
Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then a rotation matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :

@@

\begin{equation}\label{equ20}
\begin{array}{cc}
X_{k}= \left( \begin{array}{cc}
       R_{X_k} & t_{X_k} \\
       \mathbf{0}^{T} & \mathbf{1}\\
\end{array} \right),&
Y_{k}= \left( \begin{array}{cc}
       R_{Y_k} & t_{Y_k} \\
       \mathbf{0}^{T} & \mathbf{1}\\
\end{array} \right)
\end{array}
\end{equation}
where $k = 1,2,...,8$.

The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:

>>>>

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
%\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
\usepackage{mathtools}   % loads Â»amsmathÂ«
\usepackage{amssymb,amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage[normalem]{ulem}

@@

%In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem. Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams. A probabilistic method is presented to solve the homogeneous matrix equations without a priori knowledge of the correspondence. Using the Euclidean-Group invariants, an exact solution can be found. For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
Calibration is often an important and necessary step in the use of image-guided systems. In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control. As an added difficulty, the exact correspondence between the streams of sensor data ($A$'s and $B$'s) is typically unknown due to asynchrony in sampling rates and processing time. One common scenario is a constant shift between the two data streams. Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$'s and $B$'s. We begin by discussing probability density functions on $SE(3)$ and then use Euclidean-group invariants to obtain an exact solution for $X$ and $Y$. We then present a method to simultaneously recover $X$ and $Y$ and the correspondence between temporally shifted data sets using a correlation method. Following this, we show how
to solve the problem in the case when the data are completely scrambled, corresponding to a complete loss of
temporal information.
Finally, we numerically simulated the proposed method with asynchronous data and noise added to the stream of $B$'s to verify its efficiency and robustness.

@@

In the $\textbf{AX=YB}$ problem, data streams of $A$'s and $B$'s can be respectively obtained via different sensors. The data streams may arrive in an asynchronous fashion due to the different working frequencies of the sensors. This asynchrony causes a shift between the two data streams which can obscure the correspondence between the $A$'s and $B$'s. Moreover, data loss can destroy information about
 correspondence altogether. In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$'s and $B$'s.

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem formulated as AX=YB. (2) The hand-eye calibration problem formulated as AX=XB. Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems. (The Universal Robot pictured above is from the laboratory of Prof. Emad Boctor of Johns Hopkins University). 
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,rovelo2008geometric, fassi2005hand,zhao2011hand,ackerman2014online}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown a priori \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative, ernst2012non,strobl2006optimal,li2010simultaneous,shah2013solving,heller2014hand}. Simulatneous calibration %s
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange, and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a priori. In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

The rest of the paper is organized as follows. In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$. In Section \ref{sect3}, an algorithm involving both a temporal correlation calculation and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. In Section \ref{sect5}, we briefly discuss the case where one can obtain $\left( X, Y \right)$ without recovering the correspondence between the data sets.
Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.

@@

Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector,
 $T$ denotes the transpose of a vector or matrix, and $H$ is the symbol for an element of $SE(3)$
 (which is a six-dimensional Lie group) represented as a $4\times 4$ homogeneous transformation matrix.
 The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I$.

@@

\begin{equation}\label{equ1}
A_{i}X=YB_{i}.
\end{equation}
For a group element $H \in SE(3)$, a Dirac delta function $\delta(H)$ is defined to be finite only at the identity and zero elsewhere,

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{lll}
+\infty& {\rm if} & H=I \\
0& {\rm if} & H \neq I,
\end{array}
\right.
\end{equation}
and also satisfies the identity constraint

@@

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given $K,H \in SE(3)$ and two well-behaved functions $f_{1}$ and $f_{2}$, their convolution on $SE(3)$ is defined as \cite{chirikjian2011stochastic,chirikjiandover}

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H) = \int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK
\end{equation}
where $\circ$ denotes the group product for $SE(3)$, which is simply matrix multiplication.
The integral over $SE(3)$ can be expressed in various coordinates, and both the bounds of the integral and
the integration measure $dH$ will take on different appearances that depend on these coordinates.
For example, if $H$ is parameterized in terms of the Cartesian coordinates ${t} = [x,y,z]^T$,
and $R = R_{ZXZ}(\alpha,\beta,\gamma)$ is an Euler-angle description of rotations, then the
integral over $SE(3)$ is the six-dimensional integral where
$x,y,z$ range over $-\infty$ to $+\infty$, $\alpha,\gamma$ range from $0$ to $2\pi$ and $\beta$ ranges
from $0$ to $\pi$. In these coordinates, the integration measure takes the form
$$ dH = \sin\beta d\alpha d\beta d\gamma dx dy dz = dR d{t}. $$
Alternatively, exponential coordinates can be used, in which case the six-dimensional
integral over $SE(3)$ and the measure take the form described in \cite{wang2008nonparametric}.

When it is clear that the argument of a function is $H \in SE(3)$, sometimes it will be convenient to
abbreviate $f(H)$ as $f$ and $(f_{1}\ast f_{2})(H)$ as $f_{1}\ast f_{2}$ to avoid a proliferation of
parentheses.

The convolution operation is bi-linear in the sense that
$$ (a_1 f_{1} + b_1 {f'}_{1}) \ast f_{2} = a_1(f_{1} \ast f_{2}) + b_1({f'}_{1} \ast f_{2}) $$
and
$$ f_{1} \ast (a_1 f_{2} + b_1 {f'}_{2}) = a_1(f_{1} \ast f_{2}) + b_1(f_{1} \ast {f'}_{2}). $$
Moreover, convolution inherits associativity from the underlying group:
$$ f_1 \ast (f_2 \ast f_3) = (f_1 \ast f_2) \ast f_3. $$
But convolution is generally not commutative, $f_1 \ast f_2 \neq f_2 \ast f_1$.

Employing the properties of the $\delta$ function, it is straightforward to see that:

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H).
\end{equation}
Defining the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H), \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the bi-linearity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H).
\end{equation}

@@

%If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''.

The convolution of two highly-focused PDFs have some interesting properties that can be used to solve for $X$.
%For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used.
In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1}H)[\log^{\vee}(M^{-1}H)]^{T}f(H)dH \; \; \; \; \;
\IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $\log(H)$ along with its vectorized form $\log^{\vee}(H)$ are given in \cite{MLK} as

\begin{equation}
\log(H) = \widehat{\bf h}
=
\left(
\begin{array}{cccc}
   0 & -h_3 &  h_2 & h_4 \\
 h_3 &    0 & -h_1 & h_5 \\
-h_2 & -h_1 &    0 & h_6 \\
   0 &    0 &    0 &  0
\end{array}
\right)
\end{equation}
where ${\bf h} = \log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element, $\widehat{\bf h} \in se(3)$, such that $H= \exp \widehat{\bf h}$.

@@

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}\log^{\vee}(M_A^{-1}A_i)[\log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

\begin{equation}\label{equ13}
    ^{k+1}M_{A} = ^{k}M_{A} \circ \exp\left[\frac{1}{n}\sum_{i=1}^{n}\log(^{k}M_{A}^{-1}\circ A_{i})\right].
\end{equation}
An initial estimate of the iterative procedure can be chosen as: $$^{0}M_{A}=\exp\left(\frac{1}{n}\sum_{i=1}^{n}\log(A_{i})\right).$$

Alternatively,
$M_A$ can be obtained by solving a nonlinear optimization problem with the cost function
 $$ C_1(M_A) = \left\| \sum_{i=1}^{n}\log(M_{A}^{-1}A_{i}) \right\|^{2}. $$
Note, however, that mathematically this is not the same as minimizing
 $$ C_2(M_A) =  \sum_{i=1}^{n} \left\|\log(M_{A}^{-1}A_{i}) \right\|^{2}, $$
though in practice they often are minimized by very close values of $M_A$.

A similar procedure can be used to compute $M_B$. $\Sigma_A$ and $\Sigma_B$ are then straightforward to compute once $M_A$ and $M_B$ are known.

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two ``highly-focused'' functions $f_{1}$ and $f_{2}$ (i.e., those for which $\|\Sigma_i\| << 1$)
are calculated as in \cite{wang2008nonparametric}:

\begin{IEEEeqnarray}{l}\label{equ14}
M_{1 \ast 2} = M_{1}M_{2} \IEEEyessubnumber
\\*
\Sigma_{1 \ast 2} = Ad(M_{2}^{-1})\Sigma_{1}Ad^{T}(M_{2}^{-1}) + \Sigma_{2}, \IEEEyessubnumber
\end{IEEEeqnarray}
where

$$Ad(H)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right).$$
Here the ``hat'' notation when applied to the three-dimensional vector $t$ gives
\begin{equation}
\hat{t}
=
\left(
\begin{array}{ccc}
   0 & -t_3 &  t_2 \\
 t_3 &    0 & -t_1 \\
-t_2 & -t_1 &    0
\end{array}
\right)
\end{equation}

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively. Therefore, the following equations can be obtained using Eq.~(\ref{equ14}):

\begin{IEEEeqnarray}{l}
M_{A} X = Y M_{B} \IEEEyessubnumber\label{equ15a}
\\*
Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B}. \IEEEyessubnumber\label{equ15b}
\end{IEEEeqnarray}
This is a nonparametric result, meaning that the underlying probability density functions $f_A(H)$
and $f_B(H)$ need not be Gaussian or belong to any other family of parametric distributions.
Moreover, the constraint of being highly-focused is not very restrictive because the original
data sets $\{A_i\}$ and $\{B_i\}$ can always be transformed into $\{(A_i)^p\}$ and $\{(B_i)^p\}$
for some fractional power $0 < p < 1$ since
$$ A_i = X B_i X^{-1} \,\, \Longleftrightarrow \,\, (A_i)^p = X (B_i)^p X^{-1}. $$
{\color{blue} Question: this is for AX=XB, but for AX =YB, $A_i = Y B_i X^{-1}$ and the above equation doesn't apply.}

The smaller the value of $p$ is, the more concentrated the transformed data will be.

The problem of solving the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:

@@

\begin{equation}\label{equ18}
    \Lambda = (Q_{M_{A}}^{T}R_{X}^{T}Q_{M_{B}}) \Lambda (Q_{M_{B}}^{T}R_{X}Q_{M_{A}})= P \Lambda P^{T}
\end{equation}
where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. Since $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the orthogonal matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).

\begin{equation}\label{equ_P}
\left\{
\begin{array}{l}
P^{T} = P^{-1} \\
\det(P) = \pm 1.
\end{array}
\right.
\end{equation}
Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then an orthogonal matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :

@@

\begin{equation}\label{equ20}
\begin{array}{cc}
X_{k}= \left( \begin{array}{cc}
       R_{X_k} & t_{X_k} \\
       {0}^{T} & {1}\\
\end{array} \right),&
Y_{k}= \left( \begin{array}{cc}
       R_{Y_k} & t_{Y_k} \\
       {0}^{T} & {1}\\
\end{array} \right)
\end{array}
\end{equation}
where $k = 1,2,...,8$.

The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ as:
% that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:
\begin{equation}\label{equ21}
H = \left( \begin{array}{cc}
       e^{\theta \hat{n}} & ({I}_{3} - e^{\theta \hat{n}}) {p} + d{n} \\
       {0}^{T} & {1}
\end{array} \right)
\end{equation}
where $\theta$ is the angle of rotation, $d$ is the translation along the rotation axis, ${n}$ is the unit vector representing the axis of rotation and ${p}$ is the position of a point on the line relative to the origin of a space-fixed reference frame with ${ p} \cdot { n} = 0$.

Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$. Defining $B^k = X_k^{-1}Y_kB$, we have $AX_k=X_kB^k$. As discussed in \cite{chen91, ackerman2013sensor}, for $AX=XB$ problem, there exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:
